Eagle: Making multiple-locus association mapping on a genome-wide scale routine

### 2018-06-19 AM+draft.tex
19June18 rev 3

In answer to the question of how well Eagle finds true and avoids false snp-trait associations, we calculated, empirically, 
the statistical power and false discovery rates of the different methods across the six scenarios. We did this by recording the set of snp that had been used in generating a replicate's trait data. These snp are in true association with the trait. Each replicate had a different set of selected snp. 
When the data were analysed via a particular method, 
we were able to determine for that method which of its snp-trait findings were true and which were false. A snp finding was deemed to be true if it was positioned within 40 kb of the location of a true snp. Hence, 
for each method for a given replicate, we were able to record the number of true and false findings.

To calculate the power of a method, for each replicate,  the number of true snp that were found by a method is divided by the number 
of (true) snp used in generating the quantitative trait data. We then averaged across the 100 replicates. Similarly, to calculate the fdr, for 
each replicate, the number of true snp that were found is divided by the number of (true and false) snp findings for the method. We then 
averaged these power and fdr values across the 100 replicates.

To calculate the power of a method, we averaged across the 100 replicates of a scenario, the number of snp that were found by the method and true, divided by the number of true snp used in generating the quantitative trait. To calculate the false discovery rate of a method, we averaged across the 100 replicates, the number of snp that were found and true divided by the number of (true and false) snp that were found.

>>>>

In answer to the question of how well Eagle finds true and avoids false snp-trait associations, we calculated, empirically, 
the statistical power and false discovery rates of the different methods across the six scenarios. We did this by recording the set of snp that had been selected for generating a replicate's trait data. 
These snp are in true association with the trait. Each replicate had a different set of selected snp. We then determined for a method
 which of its findings were true and which were false. Those snp findings that were located within 40 kb of the location of a true snp were 
 deemed to be true.

To calculate the power of a method, we averaged across the 100 replicates of a scenario where for each replicate, we divided the number of snp findings that were true by the number of selected (true) 
snp used in generating the trait data.  Similarly, to calculate a method's fdr, we averaged across the 100 replicates of a scenario where 
for each replicate, we divide the number of true snp found by the number of (true and false) snp found.
